Computing properties of independent sets by generic programming tensor networks \thanks{\funding{...}}

### 2022-01-05 paper/paper.tex
section 2 revision

\section{Tensor networks}
Tensor network~\cite{Cirac2020, Orus2014} is also known as einsum, factor graph or sum-product network~\cite{Bishop2006} in different contexts,
it can be viewed as a generalization of matrix multiplication to multiple tensors contraction.
People often use Einstein's notation to represent a tensor network, e.g. the matrix multiplication between two matrices $A$ and $B$ can be represented in Einstein's notation as $C_{ik} = A_{ij}B_{jk}$,
where we use a label in subscripts to represent a degree of freedom.
We enumerate these degree of freedoms and accumulate the product of tensor elements to the output tensor.
In the standard notation of Einstein's summation or tensor network in physics, each index appears precisely twice.
Hence people can represent a tensor network as a simple graph,
where a tensor is a vertex and two tensors sharing the same label are connected.
In the main text, we do not have this restriction. An index can appear arbitrary times.
The graphical representation of our generalized tensor network is hypergraph, in which an edge (label) can be shared by an arbitrary number of vertices (tensors).
These two notations are equivalent in representation power because one can easily translate a generalized tensor network to the standard notation by adding $\delta$ tensors - a high dimensional equivalence of identity matrix.
However, introducing $\delta$ tensors can potentially increase the contraction complexity a lot. We illustrate this point in \App{app:tensorbad}.
\blue{Is it better to introduce the contraction orders here or in example~\ref{eg:tensorcontraction}?}

>>>>

\section{Tensor networks}
Tensor network~\cite{Cirac2020, Orus2014} is also known as einsum, factor graph or sum-product network~\cite{Bishop2006} in different contexts;
it can be viewed as a generalization of matrix multiplication to multi-dimensional tensor contraction.
Einstein's notation is often used to represent a tensor network, e.g.\ the matrix multiplication between two matrices $A$ and $B$ can be represented in Einstein's notation as $C_{ik} = A_{ij}B_{jk}$,
where we use a label in the subscript to represent a degree of freedom.
One can enumerate these degrees of freedom and accumulate the product of tensor elements to the output tensor.
In the standard notation of Einstein's summation or tensor networks in physics, each index appears precisely twice.
Hence a tensor network can be represented as a simple graph,
where a tensor is a vertex and two tensors sharing the same label are connected.
In this work, we do not impose such a restriction, so an index can appear an arbitrary number of times. 
%In the main text, we do not have this restriction. An index can appear arbitrary times.
The graphical representation of these generalized tensor networks is hypergraphs, in which an edge (label) can be shared by an arbitrary number of vertices (tensors).
These two notations are equivalent in representation power because one can easily translate a generalized tensor network to the standard notation by adding $\delta$ tensors, which is a high dimensional equivalence of the identity matrix.
However, introducing $\delta$ tensors may significantly increase the complexity of the tensor contraction. We illustrate this subtle point in \App{app:tensorbad}.
\blue{Is it better to introduce the contraction orders here or in example~\ref{eg:tensorcontraction}?}
